On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-03-27 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Add the definition of characteristic

Every integral point set has also a characteristic~\cite{kemnitz1988punktmengen,kurz2005characteristic}.
Characteristic of an IPS does not change if the set is moved, dilated ot flipped;
moreover, even addition or deletion of a point does not change the characteristic of IPS.

>>>>

Every planar IPS aso has a characteristic~\cite{kemnitz1988punktmengen,kurz2005characteristic}.

\begin{dfn}
	The characteristic of a planar integral point set $M$ is the least positive integer $q$
	such that the area of any triangle with vertices $M_1, M_2, M_3 \in M$
	is commensurable with $\sqrt{q}$.
\end{dfn}
Characteristic of an IPS does not change if the set is moved, dilated ot flipped;
moreover, even addition or deletion of a point does not change the characteristic of IPS.
